Programming Language Foundations in Agda

### 2019-07-15 papers/scp/PLFA.tex
finished segment on exams

Philip now has five years of experience teaching from SF and one year
teaching from PLFA.  He taught three courses from PLFA.
\begin{itemize}
\item
  University of Edinburgh, September--December 2018 (with teaching
  assistance from Wen and Chad Nester); twenty two-hour slots, one
  hour of lecture followed by one hour of lab. Ten students completed
  the course, which covered Parts~I and~II of PLFA.

\item
  Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio),
  March--July 2019, hosted by Roberto Ieuramalischy; ten three-hour
  slots, two hours of lecture followed by one hour of lab.  Ten
  students completed the course, which covered Parts~I and~II of PLFA,
  save students read chapter Lists on their own, and chapter
  Bisimilarity was skipped.

\item University of Padova, June 2018, hosted by Maria Emilia Maietti;
  two three-hour slots, two hours of lecture followed by one hour of
  lab.  About thirty students sat the course. Covered chapters
  Naturals, Induction, and Relations.

@@

\item
  Exercises labelled “(stretch)” are there to provide an extra
  challenge. Few students do all of these, but most attempt at least a
  few.  Ten students completed the course.

@@

Because the course is taught using a proof assistant, it is important
that the students have access to a proof assistant during the
exam. The whole point of a proof assistant is to avoid
errors. Students are told in advance that they are expected to get
perfect on the exam, and that they will have to study hard to achieve
this level.  Given that the goal of formal methods is to avoid error,
we think a pedagogical purpose is served by telling the students that
they are expected to achieve perfection and making it possible for
them to do so.

they are expected to answer
one question about formalising predicates on a data structure such
as lists or tree

The coursework is assigned 1/4 of the
total mark of the course: enough to encourage the students to do
it, but not enough to make it worth cheating. The remaining 3/4 of
the tot

Most of the marks are base

There is also a ``mock mock'' exam
assigned as cou

The coursework was broken into four or five clusters, one due every
few weeks. There is also a coursework consisting of a ``mock mock''
exam, see below.

recommended
At Edinburgh and PUC-Rio, students completed coursework based on

>>>>

Philip now has five years of experience teaching from SF and one year
teaching from PLFA.  He taught three courses from PLFA.
\begin{itemize}
\item
  University of Edinburgh, September--December 2018 (with teaching
  assistance from Wen and Chad Nester); twenty two-hour slots,
  comprising one hour of lecture followed by one hour of lab. Ten
  students completed the course, fourth-year undergraduates and
  masters.  The course covered Parts~I and~II of PLFA.

\item
  Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio),
  March--July 2019, hosted by Roberto Ieuramalischy; ten three-hour
  slots, comprising two hours of lecture followed by one hour of lab.
  Ten students completed the course, mostly doctoral students.  The
  course covered Parts~I and~II of PLFA, save students read chapter
  Lists on their own, and chapter Bisimilarity was skipped.

\item
  University of Padova, June 2018, hosted by Maria Emilia Maietti; two
  three-hour slots, comprising two hours of lecture followed by one
  hour of lab.  Thirty undergraduate students sat the course, which
  covered chapters Naturals, Induction, and Relations.

@@

\item
  Exercises labelled “(stretch)” are there to provide an extra
  challenge. Few students do all of these, but most attempt at least a
  few.

@@

Because the course is taught using a proof assistant, it is important
that students have access to a proof assistant during the exam.
Students are told in advance that they are expected to get perfect on
the exam, and that they will have to study hard to achieve this level.
Given that the goal of formal methods is to avoid error, we believe a
pedagogical purpose is served by telling the students that they are
expected to achieve perfection and making it possible for them to do
so.  Students are given two opportunities to practice in the run up to
the exam, a `mock' exam given in class under exam conditions (two
hours online), and before that a `mock mock' exam as coursework (in
their own time, encouraged to ask questions, tasked to do all three
questions rather than two of three).

Table~\ref{tab:exams} shows performance on the mock exam and the final
exam for the courses run at Edinburgh and PUC-Rio.  While scores vary
widely on the mock, all students achieve perfection on the
exam.  (The one exception was a PUC-Rio student who did not attend
classes or sit the mock.)  Similar results were achieved at Edinburgh
over the previous five years, using SF as the course textbook and Coq
as the proof assistant.  We consider these results a tribute to the
students' ability to study and learn.

\begin{table}
\begin{center}
  \begin{tabular}{|cc|cc|}
    \hline
    \multicolumn{2}{|c|}{Edinburgh} &
    \multicolumn{2}{c|}{PUC-Rio} \\
    \hline
    Mock & Exam & Mock & Exam \\
    \hline
     15  &  50  &  --  &  40  \\
     29  &  50  &  ~6  &  50  \\
     33  &  50  &  20  &  50  \\
     35  &  50  &  28  &  50  \\
     36  &  50  &  41  &  50  \\
     48  &  50  &  49  &  50  \\
     49  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
    \hline
  \end{tabular}
\end{center}
\caption{Exam marks}
\label{tab:exam}
\end{table}
